Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-04-14 reviews/response.Rmd

Q2. What is the definition of "grouping"? Though "G groups into H" was defined in Definition 5, there is not a notation of grouping $(G, H)$ until we see grouping $(day, month)$ at
Page 7 Line 7. Please rephrase the sentence each month is a grouping of the same number of days over years on Page 7 Line 5.

A2. We have used the term "pair" instead "grouping" to avoid conflict with the definition of "groups into" and rephrased the sentence.

Q3. What is the definition of aperiodic linear granularities? On Page 11, Definition 10, $M_i$ are aperiodic linear granularities. If $M_i$ are aperiodic, then is $M$ also an aperiodic linear granularity? What is the relationship between aperiodic linear granularity and aperiodic
cyclic granularity?

A3. Aperiodic linear granularities are those that can not be defined by Definition 6. If $M_i$ is periodic, then $M = \bigcup M_i$ is periodic, but if each $M_i$'s are aperiodic, then $M$ could be periodic or aperiodic. In Definition 10, we want $M$ to be aperiodic. Definition 10 and introduction of Section 3.3 briefly rephrased to improve clarity.

### 2021-04-14 main.Rmd
reviewer 2 - clarification 3 addressed

Aperiodic time granularities are those that cannot be specified as a periodic repetition of a pattern of granules. Most public holidays repeat every year, but there is no reasonably small period within which their behavior remains constant. A classic example is Easter (in the western tradition) whose dates repeat only after 5.7 million years [@Reingold2001-kf]. In Australia, if a standard public holiday falls on a weekend, a substitute public holiday will sometimes be observed on the first non-weekend day (usually Monday) after the weekend. Examples of aperiodic granularity may also include school holidays or a scheduled event. All of these are recurring events, but with non-periodic patterns. Consequently, $P_i$ (as given in \autoref{tab:quasi}) are essentially infinite for aperiodic granularities.

\begin{definition}\label{def:aperiodic}
An \textbf{aperiodic cyclic granularity} is formed when bottom granularity $B$ groups aperiodically into linear granularity $M$ such that the granularities are given by
\begin{equation}\label{eq:aperiodic}
A_{B, M}(z) = \begin{cases}
                  i, & \text{for}\quad z \in T_{i_j} \\
                  0  & \text{otherwise},
                \end{cases}
\end{equation}
where
$z$ denotes the index set,
$T_{i_j}$ are the sets of indices of $B$ describing aperiodic linear granularities $M_{i}$ such that $M_{i}(j) = \bigcup_{z \in T_{i_j}}B(z)$, and $M = \bigcup_{i=1}^{n}M_{i}$.
\end{definition}

>>>>

Aperiodic linear granularities are those that cannot be specified as a periodic repetition of a pattern of granules as described in Definition \ref{def:periodical}. Aperiodic cyclic granularities capture repetitions of these aperiodic linear granularities.
Examples include public holidays which repeat every year, but there is no reasonably small period within which their behavior remains constant. A classic example is Easter (in the western tradition) whose dates repeat only after 5.7 million years [@Reingold2001-kf]. In Australia, if a standard public holiday falls on a weekend, a substitute public holiday will sometimes be observed on the first non-weekend day (usually Monday) after the weekend. Examples of aperiodic granularity may also include school holidays or a scheduled event. All of these are recurring events, but with non-periodic patterns. Consequently, $P_i$ (as given in \autoref{tab:quasi}) are essentially infinite for aperiodic granularities.

\begin{definition}\label{def:aperiodic}
An \textbf{aperiodic cyclic granularity} is formed when bottom granularity $B$ groups into an aperiodic linear granularity $M$ such that the granularities are given by
\begin{equation}\label{eq:aperiodic}
A_{B, M}(z) = \begin{cases}
                  i, & \text{for}\quad z \in T_{i_j} \\
                  0  & \text{otherwise},
                \end{cases}
\end{equation}
where
$z$ denotes the index set,
$T_{i_j}$ are the sets of indices of $B$ describing aperiodic linear granularities $M_{i}$ such that $M_{i}(j) = \bigcup_{z \in T_{i_j}}B(z)$, and $M = \bigcup_{i=1}^{n}M_{i}$.
\end{definition}
